### 2013-08-22 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
spell check for spn chapter edits

For Jacobi-based preconditioners, convergence with MCSA is difficult
if not impossible for ill-conditioned systems with this behavior
demonstrated using a simple neutron diffusion problem. In order to
effectively solve the $SP_N$ equations for the fuel assembly problem,
a suite of preconditioners is developed and studied within the context
of MCSA. Using these preconditioners, several additional issues are
observed and alleviated to a certain extent by developing and applying
the reduced domain approximation. MCSA solutions for the fuel assembly
problem are then verified by comparing the solutions against
production Krylov solvers for problems with varying numbers of energy
groups. Finally performance is analyzed through comparison with those
same Krylov solvers in terms of both iterative performance and CPU
timing using the same set of problems utilized for the verification.

@@

%%---------------------------------------------------------------------------%%
\section{Fuel Assembly Criticality Calculations}
\label{sec:fuel_assembly_calcs}
Fuel assembly calculations are a critical piece of nuclear engineering
infrastructure for reactor core analysis and design. At this level,
individual fuel pins may be resolved at fine resolution in a variety
of configurations. As a sophisticated problem of interest to push the
limits of MCSA, a hot zero-power $17 \times 17$ pin assembly will be
used with varying energy group structure and $SP_N$ discretization in
a criticality calculation. A cross section along the vertical axis
showing homogenized fuel pin, control rod, and moderator materials and
the associated grid is given by Figure~\ref{fig:problem3_radial_mat}
while a cross section of the materials configuration along the
horizontal axis is given by Figure~\ref{fig:problem3_axial_mat}. The
control rods were removed for these problems leaving only moderator in
their place. A detailed view of the assembly bottom is given in
Figure~\ref{fig:problem3_end}. On the top and bottom of the assembly,
vacuum conditions are used as well as on the top and right boundaries
in Figure~\ref{fig:problem3_radial_mat}. Reflecting conditions are
used on the left and bottom boundaries of
Figure~\ref{fig:problem3_radial_mat}, effectively giving a
representation of one quarter of the assembly. For the spatial
discretization, each fuel pin (gray regions in
Figure~\ref{fig:problem3_radial_mat}) is resolved by a $2 \times 2$
mesh with materials and cross sections homogenized over this region.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=4in]{chapters/spn_equations/problem3_radial_mat.png}
  \end{center}
  \caption{\textbf{Fuel assembly mesh and geometry cross section.}
    \textit{Reflecting boundaries are used on the left and lower
      boundaries to create a complete $17 \times 17$ assembly
      geometry. Gray regions are homogenized fuel and red regions are
      homogenized control rods. Each fuel pin is resolved by a $2
      \times 2$ mesh.}}
  \label{fig:problem3_radial_mat}
\end{figure}
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6.0in]{chapters/spn_equations/problem3_axial_mat.png}
  \end{center}
  \caption{\textbf{Fuel assembly geometry cross section.} \textit{The
      geometry is subdivided along the axial direction into 50 zones
      spaced to capture material boundaries. Important details include
      spacer grids along the length of the fuel pins and reactor core
      structures on the top and bottom of the assembly. Lighter purple
      material in the center of the assembly is homogenized
      moderator/control rodes and darker purple/red material is
      homogenized moderator/fuel.}}
  \label{fig:problem3_axial_mat}
\end{figure}
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6.0in]{chapters/spn_equations/problem3_end.png}
  \end{center}
  \caption{\textbf{Fuel assembly geometry end detail.}
    \textit{Reactor core structure including spacer grids and plenum
      has been included. Lighter purple material on the right of the
      figure is homogenized moderator/control rods and darker
      purple/red material is homogenized moderator/fuel.}}
  \label{fig:problem3_end}
\end{figure}

@@

\subsection{ILUT Preconditioning}
\label{subsec:spn_ilut_preconditioning}
ILUT preconditioning is chosen first due to its applicability to
problems that have a dominating elliptic component such as the fuel
assembly problem or other problems with a large scattering to
absorption ratio. The algebraic formulation of ILUT requires the
physics operator to be fully formed, also a requirement for MCSA, and
is therefore easily incorporated into our solution sequence.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{4.562}{-6} & \sn{6.746}{-5} \\
      MCSA-ILUT-R-C & 0 & \sn{2.099}{-5} & \sn{2.541}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{4.812}{-5} & \sn{4.672}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.371}{-5} & \sn{2.740}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{3.605}{-5} & \sn{2.554}{-4} \\
      Richardson-ILUT & 0 & \sn{1.531}{-5} & \sn{2.771}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{7.590}{-6} & \sn{1.234}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{5.308}{-6} & \sn{1.066}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{6.388}{-5} & \sn{2.233}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{4.197}{-5} & \sn{2.168}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.736}{-5} & \sn{8.160}{-5} \\
      Richardson-ILUT & 0 & \sn{3.976}{-6} & \sn{7.059}{-5} \\
      \hline
      GMRES-ILUT & 1 & \sn{7.579}{-6} & \sn{1.246}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{1.645}{-5} & \sn{1.210}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{6.635}{-4} & \sn{9.435}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{1.797}{-4} & \sn{2.983}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{1.556}{-4} & \sn{2.055}{-4} \\
      Richardson-ILUT & 1 & \sn{4.031}{-6} & \sn{7.110}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{inf}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{2.376}{-5} & \sn{4.043}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{2.639}{-5} & \sn{3.950}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{3.958}{-5} & \sn{4.635}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.749}{-5} & \sn{3.975}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.969}{-5} & \sn{4.054}{-4} \\
      Richardson-ILUT & 0 & \sn{2.189}{-5} & \sn{3.791}{-4} \\
      \hline
      GMRES-ILUT & 1 & \sn{2.271}{-5} & \sn{3.952}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{3.701}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{3.803}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{4.142}{-5} & \sn{4.011}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{2.723}{-5} & \sn{4.030}{-4} \\
      Richardson-ILUT & 1 & \sn{2.137}{-5} & \sn{3.768}{-4} \\
      \hline
      GMRES-ILUT & 2 & \sn{2.310}{-5} & \sn{4.021}{-4} \\
      MCSA-ILUT-R-C & 2 & \sn{2.490}{-5} & \sn{3.956}{-4} \\
      MCSA-ILUT-MR-C & 2 & \sn{2.214}{-5} & \sn{3.608}{-4} \\
      MCSA-ILUT-R-EV & 2 & \sn{4.456}{-5} & \sn{3.833}{-4} \\
      MCSA-ILUT-MR-EV & 2 & \sn{3.366}{-5} & \sn{3.797}{-4} \\
      Richardson-ILUT & 2 & \sn{2.143}{-5} & \sn{3.767}{-4} \\
      \hline
      GMRES-ILUT & 3 & \sn{2.335}{-5} & \sn{4.029}{-4} \\
      MCSA-ILUT-R-C & 3 & \sn{3.045}{-5} & \sn{3.963}{-4} \\
      MCSA-ILUT-MR-C & 3 & \sn{2.696}{-5} & \sn{3.606}{-4} \\
      MCSA-ILUT-R-EV & 3 & \sn{1.947}{-5} & \sn{4.283}{-4} \\
      MCSA-ILUT-MR-EV & 3 & \sn{3.295}{-5} & \sn{3.837}{-4} \\
      Richardson-ILUT & 3 & \sn{2.161}{-5} & \sn{3.772}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g4}
\end{table}

@@

In this chapter, the Monte Carlo Synthetic Acceleration method has
been applied to the $SP_N$ discretization of the neutron transport
equation and explored in the context of a difficult nuclear fuel
assembly criticality problem. The following are the significant
observations and findings.

\begin{itemize}
\item MCSA can solve the asymmetric system generated by the $SP_N$
  equations
\item MCSA has been incorporated into the Exnihilo neutronics
  production code base developed at Oak Ridge National Laboratory
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this alone is not
  sufficient for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Light water reactor problems are difficult to solve with MCSA as
  they have large spectral radii due to the neutron scattering in the
  moderator
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations to obtain convergence with ILUT chosen for
  subsequent investigations
\item The reduced domain approximation was introduced to mitigate the
  memory and performance constraints of the explicit preconditioning
  strategy although both remain significant obstacles
\item MCSA relaxation parameters were developed and observed to
  enhance the time to solution for the fuel assembly criticality
  problem
\item MCSA was verified to produce the same k-eigenvalue for the fuel
  assembly as production Krylov methods and gave good relative flux
  agreement
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly criticality problem and
  more than Bi-CGStab using the same preconditioning
\item The explicit preconditioning strategy required to overcome the
  MCSA spectral radius restriction creates runtimes $O(100)$ larger
  than the production Krylov methods for the fuel assembly criticality
  problem
\end{itemize}

>>>>

For Jacobi-based preconditioners, convergence with MCSA is difficult
if not impossible for ill-conditioned systems with this behavior
demonstrated using a simple neutron diffusion problem. In order to
effectively solve the $SP_N$ equations for the fuel assembly problem,
a suite of preconditioners is developed and studied within the context
of MCSA. Using these preconditioners, several additional issues are
observed and alleviated to a certain extent by developing and applying
the reduced domain approximation. MCSA solutions for the fuel assembly
problem are then verified by comparing the solutions against
production Krylov solvers for problems with varying numbers of energy
groups. Finally performance is analyzed through comparison with those
same Krylov solvers in terms of both iterative performance and CPU
timing with MCSA demonstrated to have improved iterative performance
over GMRES.

@@

%%---------------------------------------------------------------------------%%
\section{Fuel Assembly Criticality Calculations}
\label{sec:fuel_assembly_calcs}
Fuel assembly calculations are a critical piece of nuclear engineering
infrastructure for reactor core analysis and design. At this level,
individual fuel pins may be resolved at fine resolution in a variety
of configurations. As a sophisticated problem of interest to push the
limits of MCSA, a hot zero-power $17 \times 17$ pin assembly will be
used with varying energy group structure and $SP_N$ discretization in
a criticality calculation. A cross section along the vertical axis
showing homogenized fuel pin, control rod, and moderator materials and
the associated grid is given by Figure~\ref{fig:problem3_radial_mat}
while a cross section of the materials configuration along the
horizontal axis is given by Figure~\ref{fig:problem3_axial_mat}. The
control rods were removed for these problems leaving only moderator in
their place. A detailed view of the assembly bottom is given in
Figure~\ref{fig:problem3_end}. On the top and bottom of the assembly,
vacuum conditions are used as well as on the top and right boundaries
in Figure~\ref{fig:problem3_radial_mat}. Reflecting conditions are
used on the left and bottom boundaries of
Figure~\ref{fig:problem3_radial_mat}, effectively giving a
representation of one quarter of the assembly. For the spatial
discretization, each fuel pin (gray regions in
Figure~\ref{fig:problem3_radial_mat}) is resolved by a $2 \times 2$
mesh with materials and cross sections homogenized over this region.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=4in]{chapters/spn_equations/problem3_radial_mat.png}
  \end{center}
  \caption{\textbf{Fuel assembly mesh and geometry cross section.}
    \textit{Reflecting boundaries are used on the left and lower
      boundaries to create a complete $17 \times 17$ assembly
      geometry. Gray regions are homogenized fuel and red regions are
      homogenized control rods. Each fuel pin is resolved by a $2
      \times 2$ mesh.}}
  \label{fig:problem3_radial_mat}
\end{figure}
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6.0in]{chapters/spn_equations/problem3_axial_mat.png}
  \end{center}
  \caption{\textbf{Fuel assembly geometry cross section.} \textit{The
      geometry is subdivided along the axial direction into 50 zones
      spaced to capture material boundaries. Important details include
      spacer grids along the length of the fuel pins and reactor core
      structures on the top and bottom of the assembly. Lighter purple
      material in the center of the assembly is homogenized
      moderator/control rods and darker purple/red material is
      homogenized moderator/fuel.}}
  \label{fig:problem3_axial_mat}
\end{figure}
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6.0in]{chapters/spn_equations/problem3_end.png}
  \end{center}
  \caption{\textbf{Fuel assembly geometry end detail.}
    \textit{Reactor core structure including spacer grids and plenum
      has been included. Lighter purple material on the right of the
      figure is homogenized moderator/control rods and darker
      purple/red material is homogenized moderator/fuel.}}
  \label{fig:problem3_end}
\end{figure}

@@

\subsection{ILUT Preconditioning}
\label{subsec:spn_ilut_preconditioning}
ILUT preconditioning is chosen first due to its applicability to
problems that have a dominating elliptic character such as the fuel
assembly problem or other problems with a large scattering to
absorption ratio. The algebraic formulation of ILUT requires the
physics operator to be fully formed, also a requirement for MCSA, and
is therefore easily incorporated into our solution sequence.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{\infty}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{4.562}{-6} & \sn{6.746}{-5} \\
      MCSA-ILUT-R-C & 0 & \sn{2.099}{-5} & \sn{2.541}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{4.812}{-5} & \sn{4.672}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.371}{-5} & \sn{2.740}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{3.605}{-5} & \sn{2.554}{-4} \\
      Richardson-ILUT & 0 & \sn{1.531}{-5} & \sn{2.771}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{\infty}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{7.590}{-6} & \sn{1.234}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{5.308}{-6} & \sn{1.066}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{6.388}{-5} & \sn{2.233}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{4.197}{-5} & \sn{2.168}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.736}{-5} & \sn{8.160}{-5} \\
      Richardson-ILUT & 0 & \sn{3.976}{-6} & \sn{7.059}{-5} \\
      \hline
      GMRES-ILUT & 1 & \sn{7.579}{-6} & \sn{1.246}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{1.645}{-5} & \sn{1.210}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{6.635}{-4} & \sn{9.435}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{1.797}{-4} & \sn{2.983}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{1.556}{-4} & \sn{2.055}{-4} \\
      Richardson-ILUT & 1 & \sn{4.031}{-6} & \sn{7.110}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_{\infty}$}} &
      \multicolumn{1}{c}{\textbf{$|| \cdot ||_2$}} \\
      \hline
      GMRES-ILUT & 0 & \sn{2.376}{-5} & \sn{4.043}{-4} \\
      MCSA-ILUT-R-C & 0 & \sn{2.639}{-5} & \sn{3.950}{-4} \\
      MCSA-ILUT-MR-C & 0 & \sn{3.958}{-5} & \sn{4.635}{-4} \\
      MCSA-ILUT-R-EV & 0 & \sn{2.749}{-5} & \sn{3.975}{-4} \\
      MCSA-ILUT-MR-EV & 0 & \sn{2.969}{-5} & \sn{4.054}{-4} \\
      Richardson-ILUT & 0 & \sn{2.189}{-5} & \sn{3.791}{-4} \\
      \hline
      GMRES-ILUT & 1 & \sn{2.271}{-5} & \sn{3.952}{-4} \\
      MCSA-ILUT-R-C & 1 & \sn{3.701}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-MR-C & 1 & \sn{3.803}{-5} & \sn{3.933}{-4} \\
      MCSA-ILUT-R-EV & 1 & \sn{4.142}{-5} & \sn{4.011}{-4} \\
      MCSA-ILUT-MR-EV & 1 & \sn{2.723}{-5} & \sn{4.030}{-4} \\
      Richardson-ILUT & 1 & \sn{2.137}{-5} & \sn{3.768}{-4} \\
      \hline
      GMRES-ILUT & 2 & \sn{2.310}{-5} & \sn{4.021}{-4} \\
      MCSA-ILUT-R-C & 2 & \sn{2.490}{-5} & \sn{3.956}{-4} \\
      MCSA-ILUT-MR-C & 2 & \sn{2.214}{-5} & \sn{3.608}{-4} \\
      MCSA-ILUT-R-EV & 2 & \sn{4.456}{-5} & \sn{3.833}{-4} \\
      MCSA-ILUT-MR-EV & 2 & \sn{3.366}{-5} & \sn{3.797}{-4} \\
      Richardson-ILUT & 2 & \sn{2.143}{-5} & \sn{3.767}{-4} \\
      \hline
      GMRES-ILUT & 3 & \sn{2.335}{-5} & \sn{4.029}{-4} \\
      MCSA-ILUT-R-C & 3 & \sn{3.045}{-5} & \sn{3.963}{-4} \\
      MCSA-ILUT-MR-C & 3 & \sn{2.696}{-5} & \sn{3.606}{-4} \\
      MCSA-ILUT-R-EV & 3 & \sn{1.947}{-5} & \sn{4.283}{-4} \\
      MCSA-ILUT-MR-EV & 3 & \sn{3.295}{-5} & \sn{3.837}{-4} \\
      Richardson-ILUT & 3 & \sn{2.161}{-5} & \sn{3.772}{-4} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The infinity norm and
      2-norm of the relative flux vector in each group is given with
      BiCGStab used as the reference.}}
  \label{tab:serial_differences_g4}
\end{table}

@@

In this chapter, the Monte Carlo Synthetic Acceleration method has
been applied to the $SP_N$ discretization of the neutron transport
equation and explored in the context of a difficult nuclear fuel
assembly criticality problem. The following are the significant
observations, findings, and contributions.

\begin{itemize}
\item MCSA can solve the asymmetric system generated by the $SP_N$
  equations
\item MCSA has been incorporated into the Exnihilo neutronics
  production code base developed at Oak Ridge National Laboratory
\item Light water reactor problems are difficult to solve with MCSA as
  they have large spectral radii due to the neutron scattering in the
  moderator
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this alone is not
  sufficient for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations to obtain convergence with ILUT chosen for
  subsequent investigations
\item The reduced domain approximation was introduced to mitigate the
  memory and performance constraints of the explicit preconditioning
  strategy although both remain significant obstacles
\item MCSA was verified to produce the same k-eigenvalue for the fuel
  assembly as production Krylov methods and gave good relative flux
  agreement
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly criticality problem and
  more than Bi-CGStab using the same preconditioning
\item The explicit preconditioning strategy required to overcome the
  MCSA spectral radius restriction creates runtimes $O(100)$ larger
  than the production Krylov methods for the fuel assembly criticality
  problem
\end{itemize}
